Conference Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-03-19 paper.tex
Make Introduction Section

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the page limits.

>>>>

\section{Introduction}

Scheduling is a crucial part in many real-time applications such as scheduling airlines and railways communications, products manufacturing processes, data packets routing in computer networks and pipe networks. Operating systems multiprocessing environments are no different than those mediums mentioned, where processes compete over CPU utilization. This brought to existence the need for scheduling algorithms to justly assign processes to available CPUs in favour of optimising performance measures, in particular, to maximize overall CPU utilization and throughput, and to minimize response time, waiting time and turnaround time. A schedular could be preemptive where it can temporarily interrupt a process without its cooperation and assign the CPU resources to a different process with the intention to assign them back to the former process, such operation is called context switching, or it could be non-preemptive (cooperative) by not being able to context switch between processes. Various preemptive and non-preemptive scheduling disciplines exist such as, first come, first serve (FCFS), shortest job first (SJF), shortest remaining time first (SRTF), round-robin (RR), multilevel queue and multilevel feedback queue. In FCFS, processes are non-preemptively executed according to their arrival time. In SJF, the CPU is assigned to the process with the smallest burst time. SRTF is a preemptive version of SJF where at each iteration, the process with the least remaining burst time takes control of the CPU. Round-robin preemptively assigns the CPU to each process in the ready queue for a static amount of time called quantum and executes them in an FCFS fashion. Multilevel queue algorithm partitions the ready queue into several queues to which processes are perpetually assigned and are executed according to another scheduling algorithm (e.g. RR). Processes cannot move from one queue to another. However, in multilevel feedback queue algorithm, processes that don't terminate in one queue, due to having CPU burst time more than the time quantum assigned to their particular queue, are shifted to a lower priority queue. Due to the fact that long processes eventually sink to the lowest priority queue, they are carried out using FCFS to prevent starvation. Several papers discuss different methods to optimize the algorithms mentioned, each come with their set of advantages and drawbacks. One of many is Paper [], whose approach achieves better average response time but at the cost of hindering the scheduling process due to recalculating time quantum for each queue using a recurrent neural network. Our proposed approach implements the best of all worlds regarding paper [] and [] by avoiding each drawback and optimising their advantages.
